yield response function

### 2025-09-21 codes/R/visualized_results.qmd
Add visualization

```{r}
plot_yield_response(model = "NO_ANN", n_fields = 5)     # uses N
plot_yield_response(model = "DO_ANN", n_fields = 5)     # uses N_tilde 
plot_yield_response(model = "SO_ANN", n_fields = 10) 
plot_yield_response(model = "NO_RF", n_fields = 5) 
plot_yield_response(model = "SO_RF", n_fields = 5) 
```
# RMSE

@@

# ---- Constants: all 18 result folders ----
MODEL_DIRS <- c(
  "CF_outcome_1_fields","CF_outcome_5_fields","CF_outcome_10_fields",
  "RANN_outcome_one_field","RANN_outcome_five_fields","RANN_outcome_ten_fields",
  "Simple_ANN_outcome_one_field","Simple_ANN_outcome_five_fields","Simple_ANN_outcome_ten_fields",
  "NO_RF_one_field","NO_RF_five_fields","NO_RF_ten_fields",
  "HalfRRF_one_field","HalfRRF_five_fields","HalfRRF_ten_fields",
  "half_RANN_outcome_one_field","half_RANN_outcome_five_fields","half_RANN_outcome_ten_fields"
)

@@

parse_n_fields <- function(folder) {
  case_when(
    str_detect(folder, "(?:_1_fields|one_field)\\b")   ~ 1L,
    str_detect(folder, "(?:_5_fields|five_fields)\\b") ~ 5L,
    str_detect(folder, "(?:_10_fields|ten_fields)\\b") ~ 10L,
    TRUE ~ NA_integer_
  )
}

@@

rmse_plot_df <- rmse_tbl_raw %>%
  filter(ok_rows, Model %in% names(model_to_row)) %>%
  mutate(
    row_lab = recode(Model, !!!model_to_row),
    col_lab = factor(`#field`,
                     levels = c(1, 5, 10),
                     labels = c("Number of fields: 1",
                                "Number of fields: 5",
                                "Number of fields: 10"))
  )

@@

# 
rmse_df <- rmse_tbl_raw %>%
  dplyr::group_by(Model, `#field`, sim) %>%  
  dplyr::summarise(RMSE = dplyr::first(RMSE), .groups = "drop") %>%
  # Rename models
  dplyr::mutate(
    Model = dplyr::recode(
      Model,
      "Simple_ANN" = "NO_ANN",
      "HalfRANN"   = "SO_ANN",
      "RANN"       = "DO_ANN",
      "HalfRRF"    = "SO_RF",
      "CF"         = "CF",
      "NO_RF"      = "NO_RF",
      .default     = Model
    ),
    field_f = factor(`#field`, levels = c(1, 5, 10),
                     labels = c("1 field", "5 fields", "10 fields"))
  )

@@

>>>>

```{r}
# plot_yield_response(model = "NO_ANN", n_fields = 5)     # uses N
# plot_yield_response(model = "DO_ANN", n_fields = 5)     # uses N_tilde 
# plot_yield_response(model = "SO_ANN", n_fields = 10) 
# plot_yield_response(model = "NO_RF", n_fields = 5) 
# plot_yield_response(model = "SO_RF", n_fields = 5)

models_to_compare <- c("NO_ANN", "DO_ANN", "SO_ANN", "NO_RF", "SO_RF")

# 
plot_yield_response("NO_ANN", 1, global_models = models_to_compare)
plot_yield_response("NO_ANN", 5, global_models = models_to_compare)
plot_yield_response("NO_ANN", 10, global_models = models_to_compare)
plot_yield_response("DO_ANN", 1, global_models = models_to_compare)
plot_yield_response("DO_ANN", 5, global_models = models_to_compare)
plot_yield_response("DO_ANN", 10, global_models = models_to_compare)
plot_yield_response("SO_ANN", 1, global_models = models_to_compare)
plot_yield_response("SO_ANN", 5, global_models = models_to_compare)
plot_yield_response("SO_ANN", 10, global_models = models_to_compare)
plot_yield_response("NO_RF",  1, global_models = models_to_compare)
plot_yield_response("NO_RF",  5, global_models = models_to_compare)
plot_yield_response("NO_RF",  10, global_models = models_to_compare)
plot_yield_response("SO_RF",  1, global_models = models_to_compare)
plot_yield_response("SO_RF",  5, global_models = models_to_compare)
plot_yield_response("SO_RF",  10, global_models = models_to_compare)
```

# RMSE

@@

# ---- Constants: all 18 result folders ----
MODEL_DIRS <- c(
  "CF_outcome_1_fields","CF_outcome_5_fields","CF_outcome_10_fields",
  "RANN_outcome_one_field","RANN_outcome_five_fields","RANN_outcome_ten_fields",
  "Simple_ANN_outcome_one_field","Simple_ANN_outcome_two_fields","Simple_ANN_outcome_three_fields", "Simple_ANN_outcome_four_fields",
  "Simple_ANN_outcome_five_fields","Simple_ANN_outcome_ten_fields","Simple_ANN_outcome_twenty_fields",
  "NO_RF_one_field","NO_RF_five_fields","NO_RF_ten_fields",
  "HalfRRF_one_field","HalfRRF_five_fields","HalfRRF_ten_fields",
  "half_RANN_outcome_one_field","half_RANN_outcome_five_fields","half_RANN_outcome_ten_fields", "half_RANN_outcome_twenty_fields"
)

@@

parse_n_fields <- function(folder) {
  case_when(
    str_detect(folder, "(?:_1_fields|one_field)\\b")      ~ 1L,
    str_detect(folder, "(?:_2_fields|two_fields?)\\b")    ~ 2L,
    str_detect(folder, "(?:_3_fields|three_fields?)\\b")  ~ 3L,
    str_detect(folder, "(?:_4_fields|four_fields?)\\b")   ~ 4L,
    str_detect(folder, "(?:_5_fields|five_fields?)\\b")   ~ 5L,
    str_detect(folder, "(?:_10_fields|ten_fields?)\\b")   ~ 10L,
    str_detect(folder, "(?:_20_fields|twenty_fields?)\\b")~ 20L,
    TRUE ~ NA_integer_
  )
}

@@

rmse_plot_df <- rmse_tbl_raw %>%
  filter(ok_rows, Model %in% names(model_to_row)) %>%
  mutate(
    row_lab = recode(Model, !!!model_to_row),
    col_lab = factor(`#field`,
                     levels = c(1, 2, 3, 4, 5, 10, 20),
                     labels = c("Number of fields: 1",
                                "Number of fields: 2",
                                "Number of fields: 3",
                                "Number of fields: 4",
                                "Number of fields: 5",
                                "Number of fields: 10",
                                "Number of fields: 20"))
  )

@@

# 
rmse_df <- rmse_tbl_raw %>%
  dplyr::group_by(Model, `#field`, sim) %>%  
  dplyr::summarise(RMSE = dplyr::first(RMSE), .groups = "drop") %>%
  # Rename models
  dplyr::mutate(
    Model = dplyr::recode(
      Model,
      "Simple_ANN" = "NO_ANN",
      "HalfRANN"   = "SO_ANN",
      "RANN"       = "DO_ANN",
      "HalfRRF"    = "SO_RF",
      "CF"         = "CF",
      "NO_RF"      = "NO_RF",
      .default     = Model
    ),
    field_f = factor(`#field`, levels = c(1, 2, 3, 4, 5, 10, 20),
                     labels = c("1 field", "2 fields", "3 fields", "4 fields",  "5 fields", "10 fields", "20 fields"))
  )

@@

# Best model by order

```{r}
library(dplyr)
library(stringr)

best_models <- rmse_summary %>%
  mutate(field_n = as.numeric(str_extract(field_f, "\\d+"))) %>%
  group_by(field_n) %>%
  #  the best model 
  slice_min(order_by = mean, with_ties = FALSE) %>%
  ungroup() %>%
  # order by RMSE 
  arrange(mean, field_n) %>%
  select(Model, field_f, mean)

## Vis

library(gt)

best_models %>%
  gt() %>%
  tab_header(
    title = "Best Models by Field Count",
    subtitle = "Ordered by lowest mean RMSE"
  ) %>%
  fmt_number(
    columns = c(mean),
    decimals = 3
  ) %>%
  cols_label(
    field_f = "# Fields",
    mean    = "mean RMSE"

  ) %>%
  tab_options(table.font.size = "small")
